Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-11-13 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Structure of section

This optimization problem was selected because is representative of the kind of
algorithms, data types and structures employed in large scale optimization problems. 
The function was implemented in both matlab and Java languages as part of  the
Test Suite of the companion competition. To give competitors an idea of the
computationa cost of the challenge, the runtime required for 10,000 function 
evaluations (FEs) was published for a particular configuration, where the Java
implementation took 7596ms and the Matlab version 1115ms. The whole experiment had
as termination condition 3,000,000 FEs. 
%---------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}

>>>>

This optimization problem was selected because is representative of the kind of
algorithms, data types and structures employed in large scale optimization problems. 
The function was implemented in both matlab and Java languages as part of  the
Test Suite of the companion competition. To give competitors an idea of the
computationa cost of the challenge, the runtime required for 10,000 function 
evaluations (FEs) was published for a particular configuration, where the Java
implementation took 7596ms and the Matlab version 1115ms. The whole experiment had
3,000,000 FEs as the termination condition. Using the Java implementation as
a guide, the function described above was implemented to compare the performence against
both implementations, again using the test of time required for 10,000 FEs. 
Before discussing the setup and performance results, certain details of
the implementation in JavaScript are presented, to give readers an idea of 
how practical and mature is the language for developing complex mathematical functions
as well as some limitations.

\begin{itemize}
\item {\em Randomize}
\item {\em Arrays} 
\item {\em Timing functions}
\item {\em Tools} 
\end{itemize}

The performance of the first test is presented in

\subsubsection{Setup of experiment in NodIO-W$^2$ }

\subsubsection{Results}

%---------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}
